Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
fix #13 #17

In addition to these exports, the simulator condenses, aggregates and saves relevant quantities on the fly to avoid having to manipulate large data volumes after the simulation. These metrics concern weather information, energy consumption and comfort assessment, and are exported in JSON format. The produced files are uploaded to a data management platform via the CI/CD pipeline, who is then in charge of notifying a different workflow in order to render insightful figures that showcase the simulation results.

Insights are presented in the form of a comprehensive report and are automatically deployed on a website built using the \textit{Antora} framework. End users are finally able to explore the simulation outputs in a detailed but malleable manner, for both the city and the building scales.

The figure \ref{fig:ktirio-cases-report} presents a gallery of city reports that are taken as test cases for the Urban Building pilot, as well as an example of a city report section showing the occlusion factor and heat flow plot.
\begin{figure}[htbp]
  \centering
  \subfloat[Gallery of test case cities reports\label{fig:city-gallery}]{%
    \includegraphics[width=0.45\textwidth]{img-compressed-city-gallery.png}
  }
  \hfill
  \subfloat[Section of a city report\label{fig:city-report-section}]{%
    \includegraphics[width=0.45\textwidth]{img-compressed-city-report-section.png}
  }
  \caption{Screenshots of the \url{https://cases.ktirio.fr} reporting website.}
  \label{fig:ktirio-cases-report}
\end{figure}

@@

@@

>>>>

@@

\subsubsection{Input data}

To run a KUB simulation, several input files need to be generated.
We have several metadata files (in JSON format), mesh data files (in MSH format), and
meteorological measurement files (in CSV format).
In the table \ref{tab:input-data-size-comparison}, we have listed these files
with their corresponding sizes.
In this comparison, we used New York City as the location
and a duration of one year for the simulation.
In addition, we compared the size of the input data with the size of the zone.

\begin{table}[h]
\begin{center}
  \begin{tabular}{|c|| c | c | c|} 
    \hline
    Files & $4 \times 4 \mathrm{km}^2$ & $10 \times 10 \mathrm{km}^2$ & $20 \times 20 \mathrm{km}^2$ \\ [0.5ex] 
    \hline\hline
    geographicdata\_setup.json & 4.0 K  & 4.0 K & 4.0 K \\ 
    \hline
    gis.json & 23 M & 117M & 470 M \\
    \hline
    mesh\_lod0.msh & 17 M & 112M & 496 M \\
    \hline
    mesh\_lod1.msh & 44 M & 240M & 896 M \\
    \hline
    weather-data-0.hourly-variables.csv & 384 K  & 384 K  & 384 K  \\
    \hline
    weather-data.json & 4.0 K  & 4.0 K & 4.0 K  \\ [1ex] 
    \hline
  \end{tabular}
\end{center}
\caption{Size comparison of input data using New York city.}
\label{tab:input-data-size-comparison}
\end{table}

@@

The total elapsed time varies from 100 seconds to 1000 seconds in function of the number of Nodes.
All machines tested have an elapsed time of the same magnitude order.
